---
title: "Guide to using eur and eurusds functions"
author: "Anna Alexandra Grigoryan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(convertcurr)
```

Using the packages `convertcurr::eurusds` and `convertcurr::eur` with the `binancer` package. Fetching the daily volume of Bitcoins sold for "USDT" on Binance and reporting the overall value of this asset in EUR. 

First we import the daily BTCUSD prices via the binancer API. 

```{r}
library(binancer)
library(data.table)
library(logger)
library(ggplot2)
library(convertcurr)

coin_prices <- binance_klines('BTCUSDT', interval = '1d', limit = 45)
balance <- coin_prices[, .(date = as.Date(close_time), btcusd = close, volume_usd = volume)]

```

Then  we calculate the value of the assets in EUR using the function `convertcurr::eurusds`.
We use the rolling join for merging the exchange rates and bitcoin volume. 

```{r}
date_to <- Sys.Date()
date_from <- Sys.Date() - 45
exchangerate <- eurusds(date_from, date_to)
setkey(balance, date)
setkey(exchangerate, date)
balance <- exchangerate[balance, roll = TRUE] ## DT[i, j, by = ...]

balance[, value := volume_usd * btcusd * eurusd]

```


Finally, we use the `ggplot2::ggplot` to visualize the value of assets in EUR for the past 45 days. Additionally, we use the `convertcurr::eur`, to have the EUR sign on the labels.

```{r}
ggplot(data = balance, aes(x = date, y = value)) +
  geom_line(color = 'blue') +
  scale_y_continuous(labels = eur)+
  theme_bw() +
  labs(title = 'Total BTC asset value in EUR in the last 45 days', x = 'EUR value', y = 'day')
```

